### 2019-11-13 paper/conceptual_framework.tex
Minor edits

The question is how birth spacing is likely to change over time and with increasing
education in India.
As other countries like the US have developed, they have seen a progressively longer 
spacing between births as the proportion of births with very short intervals---less than 
24 months---have declined substantially \citep{Hotz1997}.
Most of the these countries do, however, not have the same degree of son preference that
we see in India.

@@

The main drivers of birth spacing of interest for India are female education and
development together with son preference and the increased availability of sex selection.

>>>>

As other countries like the US have developed, they have seen a progressively longer 
spacing between births as the proportion of births with very short intervals---less than 
24 months---have declined substantially \citep{Hotz1997}.
Most of the these countries do, however, not have the same degree of son preference that
we see in India.

@@

In summary, female education affects birth spacing through a variety of pathways.
The main pathway of interest here is the effect of sex selection on spacing.
However, to understand the effects of the increased use of sex selection over time it
is important to also understand the other changes that affect birth spacing.
The most likely factors are the changes in household income/wealth and the improvements
in health as India has developed.
I, therefore, now look at how female education and labor force participation has changed
over time in India.
